\begin{recipe}[\vegan]{Lemony Couscous and Pecan Dressing With Parsley and Garlic}
    \index{lemony couscous and pecan dressing with parsley and garlic}
    \ingredient{Couscous}
    \ingredient{Pekannuss}
    \source{New York Times \cite{nyt-lemony-couscous}}
    \yield{8 to 10 servings}

    \begin{ingredients}
        \entry[1\quarter\cups]{pecan halves}
        \entry[2\half\cups]{couscous, preferably whole wheat}
        \entry[1\quarter\tsp]{fine sea salt, plus more to taste}
        \entry[\half\cup]{extra virgin olive oil}
        \entry[3\tbsp]{extra virgin olive oil}
        \entry{zest and juice of 1 lemon}
        \entry[\quarter\cup]{finely chopped scallions, white and green parts}
        \entry[1]{fat garlic clove, minced}
        \entry[1\tsp]{Turkish red pepper or Aleppo pepper}
        \entry[1\quarter\cups]{chopped parsley}
        \entry[4]{large eggs}
    \end{ingredients}

    \begin{instructions}
        Heat the oven to 325\degF.
        Spread pecans on a baking pan in one layer and toast until fragrant, about 10 minutes.
        Let cool and chop coarsely.
        Turn the oven to 350\degF.

        Meanwhile, in a large bowl, mix the couscous with 2\half~cups boiling water and \quarter~teaspoon sea salt.
        Cover and let stand 5 minutes.
        Stir in 3 tablespoons olive oil and fluff with a fork.

        Stir the lemon zest, lemon juice, scallions, garlic, red pepper and remaining teaspoon salt together in a bowl and let stand for 2 minutes.
        Add the remaining \half~cup olive oil.

        Stir the parsley, the nuts and the lemon-and-oil mixture into the couscous until combined.

        Lightly beat the eggs and mix well with the couscous mixture.
        Spoon into a 2-quart gratin dish and bake for 35 to 40 minutes, until golden brown. 
    \end{instructions}
\end{recipe}
