\begin{recipe}[\vegan]{Sesame \& Maple-Glazed Tofu}
    %with Quinoa & Vegetables
    \index{Sesame \& Maple-Glazed Tofu}
    \ingredient{Tofu}
    \ingredient{Quinoa}
    \source{\href{https://www.blueapron.com/recipes/sesame-maple-glazed-tofu-with-quinoa-vegetables}{Blue Apron}}
    \yield{2 servings}

    \begin{ingredients}
        \entry[14\oz]{firm or extra firm tofu}
        \entry[\half\cup]{red quinoa}
        \entry[4\oz]{cremini mushrooms}
        \entry[2]{scallions}
        \entry[2]{cloves garlic}
        \entry[\half\lb]{red cabbage}
        \entry[6\oz]{carrots}
        \entry[2\tbsp]{coconut aminos (seasoning sauce)}
        \entry[1\tbsp]{sesame oil}
        \entry[1]{1-inch piece ginger}
        \entry[1\half\tbsp]{maple syrup}
        \entry[1\tbsp]{white wine vinegar}
        \entry[1\tbsp]{togarashi seasoning (sweet paprika, hot paprika, dried orange peel, poppy seeds, white sesame seeds \& black sesame seeds)}
    \end{ingredients}

    \begin{instructions}
        Fill a medium pot 3/4 of the way up with salted water; cover and heat to boiling on high. Once boiling, add the quinoa and cook, uncovered, 18 to 20 minutes, or until tender. Turn off the heat. Drain thoroughly and return to the pot. 

        Meanwhile, drain the tofu, then place on a paper towel-lined plate. Place several layers of paper towels on top, then place a heavy-bottomed pot (or pan) on top of the paper towels. Set aside to release the excess liquid at least 10 minutes. 

        Meanwhile, wash and dry the fresh produce. Peel the carrots; thinly slice on an angle. Cut the mushrooms into bite-sized pieces. Cut out and discard the core of the cabbage; thinly slice the leaves. Peel and finely chop the ginger. Peel and roughly chop 2 cloves of garlic. Thinly slice the scallions, separating the white bottoms and hollow green tops. In a bowl, combine the sliced cabbage, chopped ginger, chopped garlic, and sliced white bottoms of the scallions. In a separate bowl, whisk together the coconut aminos, maple syrup, half the sesame oil, and 1 tablespoon of water. Taste, then season with salt and pepper if desired.

        In a medium pan (nonstick, if you have one), heat the remaining sesame oil on medium-high until hot. Add the sliced carrots and mushroom pieces in an even layer. Cook, without stirring, 4 to  5 minutes, or until lightly browned. Add the prepared cabbage mixture; season with salt and pepper. Cook, stirring occasionally, 2 to 3 minutes, or until softened. Add the vinegar. Cook, stirring frequently, 30 seconds to 1 minute, or until the liquid has cooked off. Turn off the heat.Transfer to the pot of cooked quinoa; stir to combine. Taste, then season with salt and pepper if desired. Cover to keep warm. Wipe out the pan. 

        Transfer the pressed tofu to a cutting board; cut lengthwise into 4 equal-sized pieces. Season with salt and pepper on both sides. In the same pan, heat 2 teaspoons of olive oil on medium-high until hot. Add the seasoned tofu pieces in an even layer. Cook 5 to 6 minutes, or until browned. Flip and cook 2 to 3 minutes, or until lightly browned. Add half the glaze (carefully, as the liquid may splatter). Cook, frequently spooning the glaze over the tofu, 1 to 2 minutes, or until the tofu is coated. Transfer to a cutting board. Cut crosswise into 1-inch pieces. Serve the finished quinoa topped with the cooked tofu and remaining glaze. Garnish with the sliced green tops of the scallions and as much of the togarashi as you’d like.
    \end{instructions}
\end{recipe}
