\begin{recipe}{Shortcut Moussaka}
    \index{Moussaka}
    \index{Shortcut Moussaka}
    \region{Griechenland}
    \ingredient{Melanzani}
    \source{New York Times \cite{nyt-shortcut-moussaka}}
    \yield{6 servings}

    \begin{ingredients}
        \entry[2]{medium eggplant (about 2 pounds), cut into \threequarter-inch cubes}
        \entry{kosher salt}
        \entry[\quarter\cup]{extra virgin olive oil}
        \entry[1\half\pound]{Yukon Gold potatoes, peeled and cut into 1-inch cubes}
        \entry[\third\cup]{whole milk}
        \entry[1]{large egg yolk}
        \entry[\threequarter\cup]{grated kefalotiri or Parmesan cheese}
        \entry[4\tbsp]{unsalted butter, at room temperature}
        \entry[\quarter\tsp]{grated nutmeg}
        \entry[1\pound]{ground lamb (or beef)}
        \entry[1]{very large onion, finely chopped}
        \entry[2]{cinnamon sticks}
        \entry[2]{garlic cloves, finely chopped}
        \entry[\quarter\tsp]{ground clove}
        \entry[2]{medium tomatoes, cored and chopped}
        \entry[\half\tsp]{pepper}
        \entry[3\tbsp]{bread crumbs} 
    \end{ingredients}

    \begin{instructions}
        In a colander, toss the eggplant and 1 teaspoon salt.
        Drain in the sink for 15 minutes.

        Heat oven to 450\degF.
        Toss the eggplant with the oil and spread on a large baking sheet.
        Roast, turning occasionally, until golden and tender, about 40 minutes.
        Reduce oven temperature to 400 degrees.

        Bring 6 cups water, the potatoes and 1 tablespoon salt to a boil in a large pot over high heat.
        Lower heat and simmer until potatoes are tender, about 20 minutes; drain and return potatoes to the warm pot.
        In a small bowl, whisk together milk and egg yolk.
        Mash potatoes with milk-egg mixture, \half~cup cheese, butter, \quarter~teaspoon salt and nutmeg.
        Taste and adjust seasonings if needed.

        In a very large skillet over medium-high heat, brown the lamb, breaking it up with a fork as it cooks.
        Season with \quarter~teaspoon salt.
        Push the meat to one side of the skillet and spoon off all but a thin layer of fat from the skillet.
        Add the onions and cinnamon sticks to the skillet.
        Cook until the onions are soft, about 5 minutes.
        Stir the lamb back into the onions and add the garlic and ground clove.
        Cook 2 minutes more.
        Stir in the tomatoes, \half~teaspoon salt, and pepper.
        Cook until tomatoes are soft and the mixture is thick, about 10 minutes.
        Stir in the eggplant.

        Spoon into a 9-inch baking dish.
        Spread the mashed potatoes over the lamb.
        Sprinkle with bread crumbs and the remaining \quarter~cup cheese.
        Bake until top is golden brown and slightly crusty, about 30 minutes.
        Cool 10 minutes before serving.
    \end{instructions}
\end{recipe}
