\begin{recipe}[\vegetarian]{Spicy Fregola Sarda}
    \index{Spicy Fregola Sarda}
    \index{pasta!Spicy Fregola Sarda}
    \ingredient{pasta}
    \ingredient{Grünkohl}
    \ingredient{Fenchel}
    \source{Blue Apron \cite{blue-apron:spicy-fregola-sarda}}
    \yield{2 servings}

    \begin{ingredients}
        \entry[2]{Eggs}
        \entry[1\cup]{Fregola Sarda Pasta}
        \entry[1]{15-Ounce Can Tomato Sauce}
        \entry[2]{Cloves Garlic}
        \entry[1]{Bulb Fennel}
        \entry[1]{Bunch Kale}
        \entry[1]{Red Onion}
        \entry[1]{Bunch Oregano}
        \entry[\half\cup]{Grated Parmesan Cheese}
        \entry[\half\tsp]{Crushed Red Pepper Flakes}
    \end{ingredients}

    \begin{instructions}
        Heat a medium pot of salted water to boiling on high. Once boiling, add the pasta and cook 10 to 14 minutes, or until tender. Turn off the heat. Drain thoroughly and return to the pot. Stir in a drizzle of olive oil and season with salt and pepper.

        While the pasta cooks, wash and dry the fresh produce. Heat a large pot of water to boiling on high. Peel and small dice the onion. Peel and mince the garlic. Cut off and discard the fennel stems; small dice the bulb. Remove and discard the kale stems; roughly chop the leaves. Pick the oregano leaves off the stems; discard the stems.

        While the pasta continues to cook, carefully add the eggs to the large pot of boiling water; cook for exactly 6 minutes. Drain the eggs and rinse under cold water for 30 seconds to 1 minute to stop the cooking process. When cool enough to handle, carefully peel the eggs and season with salt and pepper. Set aside in a warm place. Rinse and dry the pot.

        In the pot used to cook the eggs, heat 2 teaspoons of olive oil on medium-high until hot. Add the onion, garlic, fennel and as much of the red pepper flakes as you’d like, depending on how spicy you’d like the dish to be. Season with salt and pepper. Cook, stirring occasionally, 3 to 5 minutes, or until softened and fragrant. Add the kale; season with salt and pepper. Cook, stirring occasionally, 1 to 2 minutes, or until wilted.

        Add the tomato sauce and ½ cup of water to the pot of vegetables; season with salt and pepper. Cook, stirring occasionally, 5 to 7 minutes, or until thickened and slightly reduced in volume. Remove from heat.

        Add the cooked pasta and half the cheese to the pot of vegetables and tomato sauce; stir to combine. Season with salt and pepper to taste. Divide the finished pasta between 2 dishes. Garnish with the oregano and remaining cheese. Top with the cooked eggs. Enjoy!
    \end{instructions}
\end{recipe}
