\begin{recipe}{Panna Cotta}
    \index{Panna Cotta}%
    \region{Italien}%
    \ingredient{Schlagobers}%
    \source*{davidlebovitz-perfect-panna-cotta}%
    \yield{8 servings}

    \begin{ingredients}
        \entry[1\liter]{heavy cream (or half-and-half) (4\cups)}
        \entry[100\gram]{sugar (\half\cup)}
        \entry[2\tsp]{vanilla extract (or 1 vanilla bean, split lengthwise)}
        \entry[2\packets]{powdered gelatin (about 4\half\tsp)}
        \entry[6\tbsp]{cold water (90\milliliter)}
    \end{ingredients}

    \begin{instructions}
        \begin{enumerate}
            \item 
                Heat the heavy cream and sugar in a saucepan or microwave.
                Once the sugar is dissolved, remove from heat and stir in the vanilla extract.
                
                (If using a vanilla bean, scrape the seeds from the bean into the cream and add the bean pod. Cover, and let infuse for 30 minutes.
                Remove the bean then rewarm the mixture before continuing.)
            \item 
                Lightly oil eight custard cups with a neutral-tasting oil.
            \item 
                Sprinkle the gelatin over the cold water in a medium-sized bowl and let stand 5 to 10 minutes.
            \item 
                Pour the very warm Panna Cotta mixture over the gelatin and stir until the gelatin is completely dissolved.
            \item 
                Divide the Panna Cotta mixture into the prepared cups, then chill them until firm, which will take at least two hours but I let them stand at least four hours.

                If you're pressed for time, pour the Panna Cotta mixture into wine goblets so you can serve them in the glasses, without unmolding.
            \item 
                Run a sharp knife around the edge of each Panna Cotta and unmold each onto a serving plate, and garnish as desired.
        \end{enumerate}
        To make Panna Cotta with sheet gelatin: Soften 25\gram (approximately six sheets) in a liter of cold water for 5 to 10 minutes.
        Wring the sheets out and stir them into the warm Panna Cotta mixture in step \#4, until dissolved. 
    \end{instructions}
\end{recipe}
